Categorical and gradient aspects of wordlikeness\thanks{Thanks to Gene Buckley, Charles Yang, and audiences at NELS 43 for helpful comments.}

### 2012-11-18 2.tex
Small amount of writing

\noindent
This brings the theory of wordlikeness in line with the view of syntactic grammaticality presented by foundational documents like \emph{The Logical Structure of Linguistic Theory} \citep{LSLT} and \emph{Aspects in the Theory of Syntax} \citep{ASPECTS}, which posits multiple degrees of ungrammaticality arising from different types of syntactic violations.
\citet{BARRIERS} and \citet{Huang1982} propose further elaborations of this type of theory (see \citealt[43f.]{Schutze1996} for a critique).

>>>>

\noindent
This brings the theory of wordlikeness in line with the view of syntactic grammaticality presented by foundational documents like \emph{The Logical Structure of Linguistic Theory} \citep{LSLT} and \emph{Aspects of the Theory of Syntax} \citep{ASPECTS}, which posits multiple degrees of ungrammaticality arising from different types of syntactic violations.
\citet{BARRIERS} and \citet{Huang1982} propose further elaborations of this type of theory (see \citealt[43f.]{Schutze1996} for a critique).

### 2012-11-18 4.tex
Small amount of writing

\paragraph{Degemination} 
The final alternation found in English medial clusters is the simplification of geminates which is characteristic of ``level I'' morphology, and is found in the irregular /-t/ past tense (e.g., \emph{bend}/\emph{ben}[t], \emph{build}/\emph{buil}[t]) and in \emph{-ly} deadjectival derivatives (e.g., \emph{norma}[l]\emph{y}, cf. \emph{calm}[l]\emph{y}), and Latinate prefix allomorphy (\emph{SPE}:148; \citealt[102]{Borowsky1986}). \textsc{Degemination} is formalized here as a rule deleting the first of two segments agreeing on all feature values (except voice, possibly).
\label{degemx}

>>>>

\paragraph{Degemination} 
The final alternation found in English medial clusters is the simplification of geminates which is characteristic of ``level I'' morphology, and is found in the irregular /-t/ past tense (e.g., \emph{bend}/\emph{ben}[t], \emph{build}/\emph{buil}[t]), in \emph{-ly} deadjectival derivatives (e.g., \emph{norma}[l]\emph{y}, cf. \emph{calm}[l]\emph{y}), and Latinate prefix allomorphy (\emph{SPE}:148; \citealt[102]{Borowsky1986}). \textsc{Degemination} is formalized here as a rule deleting the first of two segments agreeing on all feature values (except voice, possibly).
\label{degemx}
